Nanophotonic Computational Design

### 2013-05-07 paper/paper.tex
Got the export to work.
evising paper.

\documentclass[letterpaper,10pt]{article}
\usepackage{graphicx}
\usepackage{opex3}
\usepackage{amsmath,amssymb}
\input defs.tex
\begin{document}
\title{Nanophotonic Computational Design}
\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

@@

\begin{thebibliography}{99}
\bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
    Opt. Express \textbf{20}, 7221-7236 (2012)
\bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
    ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,''
    Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
\bibitem{wonseok} W. Shin and S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
    J. of Comp. Phys \textbf{231}, 3406-3431 (2012).
\bibitem{levelset} S. Osher and R. Fedkiw, \emph{Level Set Methods and Dynamic Implicit Surfaces: 1st Edition} (Springer, 2002).
\bibitem{2dsplitter} Y. Jiao, S. Fan, and D. A. B. Miller, 
    ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).
\bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
    ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
    J. of Lightwave Tech. \textbf{25}, 151-156 (2007).
% \bibitem{fibergrating} Y. Tang, Z. Wang, L. Wosinski, U. Westergren, and S. He,
%     ``Highly efficient nonuniform grating coupler for silicon-on-insulator 
%     nanophotonic circuits,''
%     Opt. Lett. \textbf{35}, 1290-1292 (2010).
% \bibitem{ridge}  K. K. Lee, D. R. Lim, L.C. Kimerling, J. Shin, and F. Cerrina, 
%     ``Fabrication of ultralow-loss Si/SiO2 waveguides by roughness reduction,''
%     Opt. Lett. \textbf{26}, 1888-1890 (2001).
% \bibitem{pcslow} Y. A. Vlasov, M. O'Boyle, H. F. Hamann, and S. J. McNab,
%     ``Active control of slow light on a chip with photonic crystal waveguides,''
%     Nature \textbf{438}, 65-69 (2005).
% \bibitem{slotfocus} M. Lipson, 
%     ``Guiding, modulating, and emitting light on 
%     silicon-challenges and opportunities,'' 
%     J. Lightwave Technol. \textbf{23}, 4222-4238 (2005).
% \bibitem{active} J. Van Campenhout, P. Rojo Romeo, P. Regreny, C. Seassal, 
%     D. Van Thourhout, S. Verstuyft, L. Di Cioccio, J.-M. Fedeli, 
%     C. Lagahe, and R. Baets, 
%     ``Electrically pumped InP-based microdisk lasers integrated with a 
%     nanophotonic silicon-on-insulator waveguide circuit,'' 
%     Opt. Express \textbf{15}, 6744-6749 (2007).
% \bibitem{metallic} L. Tang, S. E. Kocabas, S. Latif, A. K. Okyay, 
%     D. S. Ly-Gagnon, K. C. Saraswat, and D. A. B. Miller, 
%     ``Nanometre-scale germanium photodetector enhanced by a 
%     near-infrared dipole antenna,'' 
%     Nature Photonics \textbf{2}, 226-229 (2008).
% % \bibitem{fwadia} V. R. Almeida, R. R. Panepucci, and M. Lipson, 
% %     ``Nanotaper for compact mode conversion,'' 
% %     Opt. Lett. \textbf{28}, 1302-1304 (2003) 
% % \bibitem{wwadia} S. G. Johnson, P. Bienstman,  M. A. Skorobogatiy, 
% %     M. Ibanescu1, E. Lidorikis, and J. D. Joannopoulos,
% %     ``Adiabatic theorem and continuous coupled-mode theory for 
% %     efficient taper transitions in photonic crystals,''
% %     Phys. Rev. E \textbf{66}, 066608 (2002)
% % \bibitem{deriv} F. Wang, J. S. Jensen, O. Sigmund, 
% %     ``Robust topology optimization of photonic crystal waveguides with 
% %     tailored dispersion properties.'' 
% %     J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011)
% % \bibitem{boydbook} S. Boyd, and L. Vandenberghe, 
% %     \emph{Convex Optimization} 
% %     (Cambridge University Press, 2004)
% \bibitem{prevwork} J. Lu, S. Boyd, and J. Vuckovic, 
%     ``Inverse design of a three-dimensional nanophotonic resonator,''
%     Opt. Express \textbf{19}, 10563-10750 (2011). 
% \bibitem{veronis} G. Veronis, and S. Fan, 
%     ``Theoretical investigations of compact couplers between dielectric slab 
%     waveguides and two-dimensional metal-dielectric-metal plasmonic waveguides,'' 
%     Opt. Express \textbf{15}, 1211-1221 (2007).
% \bibitem{yang} R. Yang, R. A. Wahsheh, Z. Lu, and M. A. G. Abushagur, 
%     ``Efficient light coupling between dielectric slot waveguide and plasmonic
%     slot waveguide,'' Opt. Lett. \textbf{35}, 649-651 (2010).
% \bibitem{code} \url{www.github.com/JesseLu/objective-first}
\end{thebibliography}

@@

>>>>

\documentclass[letterpaper,10pt]{article}
\usepackage{graphicx}
\usepackage{opex3}
\usepackage{amsmath,amssymb}

\newcommand{\myfig}[2]{
    \begin{figure}[!h]
    \begin{centering}
    \includegraphics[width=0.8\textwidth]{fig/#1}
    \caption{#2}\label{#1}
    \end{centering}
    \end{figure}
}

\newcommand{\Eq}[1]{Eq.~\eqref{#1}}
\newcommand{\Fig}[1]{Fig.~\ref{#1}}
\newcommand{\eq}[1]{eq.~\eqref{#1}}
\newcommand{\fig}[1]{fig.~\ref{#1}}
\newcommand{\BI}{\begin{itemize}\item}
\newcommand{\I}{\item}
\newcommand{\EI}{\end{itemize}}
\newcommand{\BEAS}{\begin{eqnarray}}
\newcommand{\EEAS}{\end{eqnarray}}
% \newcommand{\BEAS}{\begin{IEEEeqnarray}{rl}}
% \newcommand{\EEAS}{\end{IEEEeqnarray}}
\newcommand{\BSA}{\begin{subequations}\begin{align}}
\newcommand{\ESA}{\end{align}\end{subequations}}
\newcommand{\BE}{\begin{equation*}}
\newcommand{\EE}{\end{equation*}}
\newcommand{\BIT}{\begin{itemize}}
\newcommand{\EIT}{\end{itemize}}

\newcommand{\eg}{{\it e.g.}}
\newcommand{\ie}{{\it i.e.} }

\DeclareMathOperator*{\minimize}{\text{minimize}\quad}
\newcommand{\subto}{\text{subject to}\quad}
\newcommand{\T}{^\dagger}

\newcommand{\ones}{\mathbf 1}
\newcommand{\reals}{{\mbox{\bf R}}}
\newcommand{\comps}{{\mbox{\bf C}}}
\newcommand{\integers}{{\mbox{\bf Z}}}
\newcommand{\symm}{{\mbox{\bf S}}}  % symmetric matrices

\newcommand{\nullspace}{{\mathcal N}}
\newcommand{\range}{{\mathcal R}}
\newcommand{\Rank}{\mathop{\bf Rank}}
\newcommand{\Tr}{\mathop{\bf Tr}}
\newcommand{\diag}{\mathop{\bf diag}}
\newcommand{\lambdamax}{{\lambda_{\rm max}}}
\newcommand{\lambdamin}{\lambda_{\rm min}}

\newcommand{\Expect}{\mathop{\bf E{}}}
\newcommand{\Prob}{\mathop{\bf Prob}}
\newcommand{\Co}{{\mathop {\bf Co}}} % convex hull
\newcommand{\dist}{\mathop{\bf dist{}}}
\newcommand{\argmin}{\mathop{\rm argmin}}
\newcommand{\argmax}{\mathop{\rm argmax}}
\newcommand{\epi}{\mathop{\bf epi}} % epigraph
\newcommand{\Vol}{\mathop{\bf vol}}
\newcommand{\dom}{\mathop{\bf dom}} % domain
\newcommand{\intr}{\mathop{\bf int}}

\begin{document}

\title{Nanophotonic Computational Design}
\author{Jesse Lu$^\ast$ and Jelena Vu\v{c}kovi\'{c}}
\address{Stanford University, Stanford, California, USA.}
\email{jesselu@stanford.edu}

@@

\begin{thebibliography}{99}
\bibitem{lipson} 
    A. Gondarenko, and M. Lipson, 
    ``Low modal volume dipole-like dielectric slab resonator,'' 
    Opt. Express \textbf{16} 17689-17694 (2008).  
\bibitem{yablo} C.-Y. Kao, S. Osher, and E. Yablonovitch, 
    ``Maximizing band gaps in two-dimensional photonic crystals by using level set methods,'' Appl. Phys. B \textbf{81}, 235-244 (2005).
\bibitem{levi}
    P. Seliger, M. Mahvash, C. Wang, and A. Levi,
    ''Optimization of aperiodic dielectric structures,''
    J. Appl. Phys. \textbf{100}, 34310-6 (2006).
\bibitem{johnson} A. Oskooi, A. Mutapcic, S. Noda, J. D. Joannopoulos, S. P. Boyd, and S. G. Johnson, 
    ``Robust optimization of adiabatic tapers for coupling to slow-light photonic-crystal waveguides,'' Opt. Express \textbf{20}, 21558-21575 (2012).
\bibitem{sigmund1} Y. Elesin, B. S. Lazarov, J. S. Jensen, O. Sigmund, 
    ``Design of robust and efficient photonic switches using topology optimization,''
    Photonics and Nanostructures - Fundamentals and Applications \textbf{10}, 
    153–165 (2012).
\bibitem{jameson} L. Martinelli, and A. Jameson, 
    ``Computational Aerodynamics: Solvers and Shape Optimization,''
    J. Heat Transfer \textbf{135}, 011002 (2013).
\bibitem{bendsoe} M. P. Bendsoe, O. Sigmund,
    ``Material interpolation schemes in topology optimization,''
    Archive of Applied Mechanics \textbf{69}, 635-654 (1999).
\bibitem{miller} D. A. B. Miller, 
    ``All linear optical devices are mode converters,'' 
    Opt. Express \textbf{20}, 23985-23993 (2012).
\bibitem{ob1_wg} J. Lu, J. Vuckovic, ``Objective-first design of high-efficiency, small-footprint couplers between arbitrary nanophotonic waveguide modes,'' 
    Opt. Express \textbf{20}, 7221-7236 (2012)
\bibitem{admm} S. Boyd, N. Parikh, E. Chu, B. Peleato, and J. Eckstein,
    ``Distributed Optimization and Statistical Learning via the Alternating Direction Method of Multipliers,''
    Foundations and Trends in Machine Learning \textbf{3}, 1-122 (2011). 
\bibitem{wonseok} W. Shin and S. Fan, ``Choice of the perfectly matched layer boundary condition for frequency-domain Maxwell’s equations solvers,''
    J. of Comp. Phys \textbf{231}, 3406-3431 (2012).
\bibitem{levelset} S. Osher and R. Fedkiw, \emph{Level Set Methods and Dynamic Implicit Surfaces: 1st Edition} (Springer, 2002).
\bibitem{2dsplitter} Y. Jiao, S. Fan, and D. A. B. Miller, 
    ``Demonstrations of systematic photonic crystal design and optimization by low rank adjustment: an extremely compact mode separator'', Opt. Lett. \textbf{30}, 140-142 (2005).
\bibitem{mode1} J. Castro, D. F. Geraghty, S. Honkanen, C. M. Greiner, D. Iazikov, and T. W. Mossberg, ``Demonstration of mode conversion using anti-symmetric waveguide Bragg gratings,'' Opt. Express \textbf{13}, 4180-4184 (2005).
\bibitem{mode2} E. Khoo, A. Liu, and J. Wu, ``Nonuniform photonic crystal taper for high-efficiency mode coupling,'' Opt. Express \textbf{13}, 7748-7759 (2005).
\bibitem{mode3} P. Sanchis, J. Marti, J. Blasco, A. Martinez, and A. Garcia, ``Mode matching technique for highly efficient coupling between dielectric waveguides and planar photonic crystal circuits,'' Opt. Express \textbf{10}, 1391-1397 (2002). 
\bibitem{forchel} T. D. Happ, M. Kamp, and A. Forchel, 
    ``Photonic crystal tapers for ultracompact mode conversion,'' 
    Opt. Lett. \textbf{26}, 1102-1104 (2001) 
\bibitem{baets}F. Van Laere, G. Roelkens, M. Ayre, J. Schrauwen, D. Taillaert, D. Van Thourhout, T. F. Krauss, and R. Baets,
    ``Compact and highly efficient grating couplers between optical fiber and nanophotonic waveguides,''
    J. of Lightwave Tech. \textbf{25}, 151-156 (2007).
\bibitem{robust1} F. Wang, J. S. Jensen, and O. Sigmund, ``Robust topology optimization of photonic crystal waveguides with tailored dispersion properties,'' J. Opt. Soc. Am. B \textbf{28}, 387-397 (2011).
\end{thebibliography}

@@

Increasingly sophisticated optimization strategies for 
    specific nanophotonic devices have been developed;
    ranging from the use of genetic algorithms\cite{lipson},
    level-set methods\cite{yablo}, 
    tweaking the size and shape of specific canonical gemetric shapes\cite{levi,johnson},
    and even utilizing the full parameter space\cite{sigmund1}.

    \cite{jameson}
    \cite{bendsoe}
